---
title: "ANOVA"
author: "Tykera Goins"
format: html
editor: visual
execute:
  warning: false
  message: false
  echo: false
---

```{r}
library(tidyverse)
```

```{r}
training <- read_csv("training.csv")
```

# Training Type and Performance Score Analysis

```{r}
ggplot(training, aes(training_type , performance_score)) +
  geom_boxplot() +
  labs(title = "Training Performance", 
       x = "Training Type",
       y = "Performance Score") +
  theme_light()
```

#### One Way ANOVA

HO: There are no differences between the means of the training type and performance score groups.

HA: There is at least one difference between the means of the training type and performance score groups.

```{r}

OWtraining <- aov(performance_score ~ training_type, training)
summary(OWtraining)
```

My interpretation following the one way ANOVA testing is there is at least one difference in means between the training type and performance score groups.

#### Two Way ANOVA

HO: There are no differences between the means of the training type and performance score groups when the experience level is considered.

HA: There is at least one difference between the means of the training type and performance score groups when the experience level is considered.

```{r}

TWtraining <- aov(performance_score ~ training_type * experience_level, training)
summary(TWtraining)
```

My interpretation following the two way ANOVA testing is there is at least one difference in means between the training type and performance score groups when experience level is considered.

```{r}
satisfaction <- read_csv("satisfaction.csv")
```

# Service and Satisfaction Score Analysis

```{r}

ggplot(satisfaction, aes(service_type , satisfaction_score)) +
  geom_boxplot() +
  labs(title = "Service Satisfaction",
       x = "Service",
       y = "Satisfaction Score") +
  theme_light()
```

#### One Way ANOVA

HO: There are no means difference between the service type and satisfaction score groups

HA: There is at least one difference in means between the service type and satisfaction score groups

```{r}
OWsatisfaction <- aov(satisfaction_score ~ service_type, satisfaction)
summary(OWsatisfaction)
```

My interpretation following the one way ANOVA testing, is there is at least one difference in means between the performance score and service type groups.

#### Two Way ANOVA

HO: There are no means difference between the service type and satisfaction score groups when the region is considered.

HA: There is at least one difference in means between the service type and satisfaction score groups when the region is considered.

```{r}

TWsatisfaction <- aov(satisfaction_score ~ service_type * region, satisfaction )
summary(TWsatisfaction)
```

My interpretation following the two way ANOVA testing is there is at least one difference in means between the performance score and service type groups when the region is considered.

#Thank you
