---
title: ""
author: "Tykera Goins"
format: pdf
execute: 
  echo: false
  warning: false
  message: false
editor: source
---

```{r}
library(tidyverse)

crime <- read_csv("crime.csv")
```

```{=tex}
\begin {minipage} {0.3 \textwidth}
\includegraphics[width=1.8in]{city.png}
\end{minipage}
\begin{minipage} {0.7\textwidth}
City Overview \\
2024 Public Admin Drive \\
Atlanta, Georgia 30322 \\
Phone: (404) 712 6308 \\
Email: cityoverview@publicadmin.org
\end{minipage}
```
### Crime Rates and Public Safety Spending

```{r}
#| fig-align: "center"


ggplot(crime, aes(spending, crime)) +
  geom_point(color = "black") +
  labs(title = "Scatterplot: Public Safety Spending and Crime Rates", 
       x = "Public Safety Spending (in million dollars)",
y = "Crime Rate (per 1,000 residents)") +
  theme_light() +
  theme(text = element_text(size = 8, family = "serif"))
```

```{r}
model1 <- lm(crime~spending, crime)

intercept <- coef(model1)
slope <- coef(model1)
r_squared <- summary(model1)$r.squared
```

A basic regression was conducted and the crime rate coefficient indicates that for every million dollar spent on public safety, the crime rate increases by an average of `r round(slope, 2)` per 1,000 residents. This result is statistically significant. The R squared value suggests that approximately `r round(r_squared * 100, 2)` % of the variability in crime rays can be explained by the amount of public safety spending.

```{r}
park <- read_csv("park.csv")
```

### Park Area Satisfaction

```{r}

ggplot(park, aes(area, satisfaction)) +
  geom_point(color = "black") +
  labs(title = "Scatterplot: Resident Satisfaction on Park Areas", 
       x = "Park Area (in acres)",
y = "Resident Satisfaction (survey score)") +
  theme_light() +
  theme(text = element_text(size = 8, family = "serif"))
```

```{r}
model2 <- lm(satisfaction~area, park)

intercept <- coef(model2)
slope <- coef(model2)
r_squared <- summary(model2)$r.squared
```

A basic regression was conducted and the resident satisfaction coefficient to the park area has an average of `r round(slope, 2)` of a survey score. This result is not statistically significant. The R squared value suggests that approximately `r round(r_squared * 100, 2)` % of the variability in resident satisfaction cannot be explained by the park area acreage.

```{r}

traffic <- read.csv("traffic.csv")
```

### Traffic Congestion Air Quality Index

```{r}
#| fig-pos: h
ggplot(traffic, aes(traffic, aqi)) +
  geom_point(color = "black") +
  labs(title = "Scatterplot: Traffic Congestion AQI", 
       x = "Traffic Congestion (in average daily hrs)",
y = "Air Quality Index") +
  theme_light() +
  theme(text = element_text(size = 8, family = "serif"))
```

```{r}
model3 <- lm(aqi~traffic, traffic)

intercept <- coef(model3)
slope <- coef(model3)
r_squared <- summary(model3)$r.squared
```

A basic regression was conducted and the AQI coefficient indicates that for every daily hour in traffic congestion, the air quality index decreases by an average of `r round(slope, 2)`. This result is statistically significant. The R squared value suggests that approximately `r round(r_squared * 100, 2)` % of the variability in poor air quality can be explained by the average daily hours spent in traffic congestion.

#thank you
